%-------------------------
% Resume in Latex
% Author : Sohil Ladhani
% License : MIT
%------------------------

\documentclass{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%---------------------------------------------------------
%%%%%%  Resume STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/sohilladhani}{\large Sohil Ladhani}} & Email : \href{mailto:sohilladhani@gmail.com}{sohilladhani@gmail.com}\\
  \href{https://www.linkedin.com/in/sohilladhani/}{https://www.linkedin.com/in/sohilladhani} & Mobile : +91 9573236099 \\
  & \href{https://www.sohilladhani.com}{www.sohilladhani.com}
\end{tabular*}

\vspace{-5pt}
%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

\resumeSubheading
      {Cisco Systems}{Bengaluru}
      {Software Engineer 2}{March 2019 - Present}
      \resumeItemListStart
        \resumeItem{License Manager}
          {Part of the team responsible for maintaining license manager code for Data Center Switches.}
        \resumeItem{Automation}
		{Led a team to develop end-to-end sanity scripts, which improved the turn around time to commit the code by 68\%, by making the sanity scripts a part of the developer workflow by deploying the scripts to a CI/CD pipeline.}
        \resumeItem{\underline{Leveraged knowledge in}}
          {C, Python, PyATS, Data Center Networks}  
      \resumeItemListEnd

    \resumeSubheading
      {Cisco Systems}{Bengaluru}
      {Network Engineer}{Jul 2017 - March 2019}
      \resumeItemListStart
        \resumeItem{Core developer}
          {Core member of Tracker and Operations Platform, which is a unified platform to track end-to-end customer deliverables. Helped reduce the delivery time to 74\% of the previous time.} 
        \resumeItem{Trusted Advisor}
          {Responsible for analyzing potential issues in the network of the European customers, and suggesting proactive countermeasures to avoid and mitigate those issues.}
         \resumeItem{\underline{Leveraged knowledge in}}
          {Python, Django, JavaScript} 
      \resumeItemListEnd

    \resumeSubheading
    {Cisco Systems}{Bengaluru}
    {Software Engineer, Intern}{Jan 2017 - Jun 2017}
      \resumeItemListStart
        \resumeItem{UT framework for Cisco IOS-XE stack}
          {Developed a module within UT framework responsible for capturing and replaying database configuration of a Cisco Catalyst switch onto a virtual environment to perform white-box testing.}
        \resumeItem{Simulation of device configurations}
          {Built an XML Parser in 'C' to parse the device configurations and simulate the same in the virtual environment. Wrote test-cases and prepared mocks for different components using Lua script.}
        \resumeItem{\underline{Leveraged knowledge in}}
          {C, Lua, Simple API for XML (libxml2)}  
      \resumeItemListEnd

    \resumeSubheading
    {BITS Pilani, Hyderabad}{Hyderabad}
      {Teaching Assitant}{Aug 2015 - Dec 2016}
      \resumeItemListStart
        \resumeItem {Java Hands-on Lab}
          {Designed assignments and supervised the lab sessions attended by 250+ students regularly.}
        \resumeItem {Distributed Operating Systems}
          {Helped instructor in charge in setting up and evaluating the examination papers.}
        \resumeItem{\underline{Leveraged knowledge in}}
          {Core Java, RPC, C}
      \resumeItemListEnd    

    \resumeSubheading
      {Thomson Reuters}{Ahmedabad}
      {Associate Software Engineer}{Aug 2013 - Oct 2014}
      \resumeItemListStart
        \resumeItem{Developer}
          {Served as a developer of AgileTax, a leading software from the tax preparation portfolio. Was responsible for developing and testing new features as per business requirements.}
        \resumeItem{Build Automation Lead}
          {Improved the daily, weekly and bi-weekly software builds by over 30\% by fully automating the build process using Microsoft Team Foundation Server.}
        \resumeItem{\underline{Leveraged knowledge in}}
          {C\# .NET, VB6}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}

  \begin{itemize}
    \item \small{{\textbf{Brainf**k Interpreter}}\vspace{-8pt}}
    \begin{itemize}
      \item \small{{Developed a web-based interpreter for brainf**k language in Python.\vspace{-3pt}}}
      \item \small{{Incorporated Python Lex-Yacc (PLY) for Lexical and Syntactical analysis of the Brainf**k source code.\vspace{-3pt}}}
      \item \small{{\textbf{\underline{Utilized:}} Python, CherryPy web framework, PLY, HTML, CSS, JavaScript\vspace{-3pt}}}
    \end{itemize}
  \end{itemize}

  \begin{itemize}
    \item \small{{\textbf{Yet Another Network Controller} (Opensource Contribution)}\vspace{-8pt}}
    \begin{itemize}
      \item \small{{Submitted a patch to Yet Another Network Controller (yanc).\vspace{-3pt}}}
      \item \small{{Modified the code to conform to OpenFlow 1.1 by changing the size of the incoming packets of the OpenFlow switch.\vspace{-3pt}}}
      \item \small{{\textbf{\underline{Utilized:}} C++, OpenFlow protocol, SDN\vspace{-3pt}}}
    \end{itemize}
  \end{itemize}

  \begin{itemize}
    \item \small{{\textbf{Simulation and Performance Analysis of Wireless SDN}}\vspace{-8pt}}
    \begin{itemize}
      \item \small{{Simulated a wireless SDN to analyze the potential advantages of SDN over wireless networks.\vspace{-3pt}}}
      \item \small{{Successfuly tested 2 techniques of mobile handoffs: 1. Proactive and 2. Reactive.\vspace{-3pt}}}
      \item \small{{\textbf{\underline{Utilized:}} Python, POX (controller), OpenNet (simulator), NetAnim (topologies)\vspace{-3pt}}}
    \end{itemize}
  \end{itemize}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Birla Institute of Technology and Science, Pilani}{Hyderabad, India}
      {Master of Engineering in Computer Science;  CGPA: 9.08}{Aug 2015 -- Jun 2017}
      
  \resumeSubheading
      {Gujarat Technological University}{Gujarat, India}
      {Bachelor of Engineering in Computer Science;  CGPA: 8.15}{Aug 2009 -- Jun 2013}
    
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \small{\textbf{Languages}{: (proficient) Java, C, (working knowledge) Python (familiar) Javascript, SQL  }\vspace{-5pt}}
   }
   \item{
     \small{\textbf{Tools}{: Git, GDB, Valgrind, Packet Tracer, Docker} \vspace{-5pt}}
   }
   \item{
     \small{\textbf{Frameworks/Libraries}{: nltk, CherryPy, Django, StAX, pickle, SAX, pip, Hadoop, libxml2} \vspace{-5pt}}
   }
 \resumeSubHeadingListEnd

 %--------CERTIFICATIONS------------
%\section{Certifications}
% \resumeSubHeadingListStart
%   \item{Cisco Certified Network Associate (CCNA)}
% \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
